% ══════════════════════════════════════════════
% CHAPTER 3: WHY 5SIM.NET — BANGLADESH PERSPECTIVE
% ══════════════════════════════════════════════

\chapter{Why 5sim.net --- The SMS Provider Decision}

\section{The Problem We Are Solving}

In Bangladesh and South Asia, there is an enormous demand for virtual phone numbers to verify accounts on platforms like Facebook, Instagram, and WhatsApp. The challenges include:

\begin{enumerate}
    \item \textbf{Local SIM card limitations:} Bangladeshi SIM cards require NID (National ID) registration, limiting how many numbers one person can have.
    \item \textbf{Number recycling:} Previously used numbers on platforms like Facebook get flagged or banned.
    \item \textbf{International number requirement:} Many platforms trust international numbers (US, UK, European) more than local numbers.
    \item \textbf{Unreliable free services:} Public OTP bots are slow, unreliable, and shared among thousands of users. The numbers are often already used.
    \item \textbf{Privacy concerns:} Using your personal number for multiple accounts creates security risks.
\end{enumerate}

\begin{importantbox}
The core requirement is: \textbf{Fresh, unused virtual phone numbers that can reliably receive OTPs on demand.} This is exactly what 5sim.net provides.
\end{importantbox}

% ──────────────────────────────────────────────
\section{What is 5sim.net?}

\href{https://5sim.net}{5sim.net} is a professional virtual SMS receiving service that provides temporary phone numbers for online verification. Key facts:

\begin{table}[H]
\centering
\caption{5sim.net at a Glance}
\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Feature} & \textbf{Details} \\
\hline
Founded & 2019, operational for 7+ years \\
\hline
Countries & 200+ countries including Bangladesh, India, USA, UK, Ethiopia \\
\hline
Services & 600+ services (Facebook, Google, WhatsApp, Instagram, etc.) \\
\hline
API & RESTful API with JWT authentication \\
\hline
Pricing & Pay-per-number; ranges from \$0.02 to \$1.00 depending on country/service \\
\hline
Payment Methods & Cryptocurrency (Bitcoin, USDT), credit cards, PayPal \\
\hline
Minimum Deposit & As low as \$1.00 \\
\hline
Uptime & 99.5\%+ availability \\
\hline
\end{tabularx}
\end{table}

% ──────────────────────────────────────────────
\section{Why We Chose 5sim.net Over Alternatives}

We evaluated multiple SMS API providers before choosing 5sim.net:

\subsection{Comparison Table}

\begin{table}[H]
\centering
\caption{SMS Provider Comparison}
\begin{tabularx}{\textwidth}{|l|c|c|c|c|X|}
\hline
\textbf{Feature} & \textbf{5sim.net} & \textbf{SMS-Activate} & \textbf{SMSPVA} & \textbf{TextVerified} \\
\hline
Countries & 200+ & 180+ & 50+ & 30+ \\
\hline
Price (Facebook) & \$0.05--0.30 & \$0.10--0.50 & \$0.15--0.40 & \$0.50--2.00 \\
\hline
API Quality & Excellent & Good & Average & Good \\
\hline
Crypto Payment & Yes & Yes & Limited & No \\
\hline
Min. Deposit & \$1 & \$1 & \$5 & \$10 \\
\hline
Auto-refund & Yes & Yes & No & Yes \\
\hline
Bangladesh Access & Full & Full & Limited & Limited \\
\hline
Documentation & Excellent & Good & Poor & Good \\
\hline
\end{tabularx}
\end{table}

\subsection{Key Reasons for Choosing 5sim.net}

\begin{enumerate}
    \item \textbf{Best Price-to-Reliability Ratio:}
    
    5sim.net offers some of the lowest prices in the market while maintaining high success rates. For Facebook verification, numbers cost as low as \$0.05--\$0.10, compared to \$0.50+ on premium providers.

    \item \textbf{Cryptocurrency Payments (Critical for Bangladesh):}
    
    \begin{warningbox}
    This is the most important factor for Bangladesh-based operations. Due to international payment restrictions in Bangladesh, many services that only accept credit cards or PayPal are difficult to use. 5sim.net accepts:
    \begin{itemize}
        \item Bitcoin (BTC)
        \item USDT (Tether --- TRC20, ERC20)
        \item Ethereum (ETH)
        \item Litecoin (LTC)
        \item Other cryptocurrencies
    \end{itemize}
    This means your team can fund the account using cryptocurrency exchanges available in Bangladesh (like Binance P2P).
    \end{warningbox}

    \item \textbf{Extensive Country Coverage:}
    
    200+ countries means you always have options. If Ethiopian numbers are temporarily unavailable, you can instantly switch to Nigerian, Kenyan, or Indonesian numbers.

    \item \textbf{Automatic Refunds:}
    
    If a number fails to receive an OTP within the time limit, 5sim.net automatically refunds the cost. Our bot also handles this --- if OTP times out, the balance is refunded to the user.

    \item \textbf{Clean API with JWT Authentication:}
    
    The API is RESTful, well-documented, and uses industry-standard JWT tokens. This made integration straightforward and secure.

    \item \textbf{High Number Availability:}
    
    Unlike smaller providers that frequently run out of stock, 5sim.net maintains a large pool of numbers across all countries.
\end{enumerate}

% ──────────────────────────────────────────────
\section{How to Purchase \& Fund 5sim.net}

\subsection{Step 1: Create an Account}

\begin{enumerate}
    \item Visit \href{https://5sim.net}{https://5sim.net}
    \item Click ``Sign Up'' or ``Register''
    \item Use email or sign in with Google/GitHub
    \item Verify your email address
\end{enumerate}

\subsection{Step 2: Get Your API Key}

\begin{enumerate}
    \item Log in to your 5sim.net account
    \item Go to \textbf{Profile} (click your username in the top right)
    \item Scroll down to \textbf{``API Key''} section
    \item Click \textbf{``Generate API Key''}
    \item Copy the key --- you will need this for the bot's \texttt{.env} file
\end{enumerate}

\begin{importantbox}
\textbf{Never share your API key with anyone.} Anyone with your key can spend your balance. Store it only in the \texttt{.env} file on your server.
\end{importantbox}

\subsection{Step 3: Fund Your Account}

This is the step that requires actual money. Here's how to do it from Bangladesh:

\subsubsection{Method 1: Binance P2P $\rightarrow$ USDT $\rightarrow$ 5sim (Recommended)}

\begin{enumerate}
    \item \textbf{Buy USDT on Binance P2P:}
    \begin{itemize}
        \item Open Binance app
        \item Go to P2P Trading
        \item Buy USDT using bKash, Nagad, or bank transfer (BDT to USDT)
        \item Typical rate: 1 USDT = 118--122 BDT
    \end{itemize}
    
    \item \textbf{Send USDT to 5sim.net:}
    \begin{itemize}
        \item On 5sim.net, go to \textbf{Payments} $\rightarrow$ \textbf{Deposit}
        \item Select \textbf{USDT (TRC20)} --- this has the lowest fees
        \item Copy the deposit address
        \item In Binance, withdraw USDT to that address (TRC20 network)
        \item Wait for confirmation (usually 1--5 minutes)
    \end{itemize}
    
    \item \textbf{Verify balance:}
    \begin{itemize}
        \item Your 5sim.net balance should update within minutes
        \item The bot can check this via the API: \texttt{sms\_provider.get\_balance()}
    \end{itemize}
\end{enumerate}

\subsubsection{Method 2: Direct Cryptocurrency}

If you already hold cryptocurrency:
\begin{enumerate}
    \item Go to 5sim.net $\rightarrow$ Payments $\rightarrow$ Deposit
    \item Select your cryptocurrency (BTC, ETH, LTC, etc.)
    \item Send the amount to the provided address
    \item Wait for blockchain confirmation
\end{enumerate}

\subsection{Step 4: Budget Planning}

\begin{table}[H]
\centering
\caption{Cost Estimation for 5sim.net}
\begin{tabularx}{\textwidth}{|l|c|c|X|}
\hline
\textbf{Scenario} & \textbf{Numbers/Day} & \textbf{Cost/Day} & \textbf{Monthly Cost (30 days)} \\
\hline
Light usage & 10 & \$0.50--\$3.00 & \$15--\$90 \\
\hline
Medium usage & 50 & \$2.50--\$15.00 & \$75--\$450 \\
\hline
Heavy usage & 200 & \$10.00--\$60.00 & \$300--\$1,800 \\
\hline
\end{tabularx}
\end{table}

\begin{tipbox}
Start with a \textbf{\$10 deposit} (approximately 1,200 BDT). This will give you 50--200 numbers depending on the countries you choose. Ethiopian and Indonesian numbers are the cheapest.
\end{tipbox}

% ──────────────────────────────────────────────
\section{Why This Creates a Zero-Error OTP System}

The combination of 5sim.net + Active Dream Bot creates a highly reliable system because:

\begin{enumerate}
    \item \textbf{Fresh Numbers Every Time:}
    
    Every number from 5sim.net is a \textbf{fresh, unused number}. It has never been registered on the target platform before. This eliminates the ``number already used'' error that plagues public OTP bots.

    \item \textbf{Dedicated Numbers:}
    
    Unlike shared/public services, when our bot purchases a number, it is \textbf{exclusively assigned to that user}. No one else can receive the OTP.

    \item \textbf{Real Carrier Numbers:}
    
    5sim.net uses numbers from real mobile carriers, not VoIP numbers. Platforms like Facebook are increasingly blocking VoIP numbers. Real carrier numbers have a much higher acceptance rate.

    \item \textbf{Automatic Retry \& Refund:}
    
    If an OTP fails to arrive:
    \begin{itemize}
        \item The bot automatically cancels the number after 5 minutes
        \item The user's balance is automatically refunded
        \item The user can immediately try another country/number
        \item 5sim.net also refunds on their end
    \end{itemize}

    \item \textbf{Multiple Country Fallback:}
    
    If numbers from one country are temporarily unavailable or not working, users can instantly switch to another country. With 200+ countries, there is always an available option.

    \item \textbf{Private \& Controlled:}
    
    Since the bot is private (admin-approved only), there is no abuse from random users. This keeps the system clean and prevents the API key from being drained by unauthorized users.

    \item \textbf{Full Audit Trail:}
    
    Every number purchase, OTP reception, and balance change is logged in the database. If something goes wrong, admins can trace exactly what happened.
\end{enumerate}

\begin{successbox}
\textbf{Expected Success Rate:} Based on 5sim.net's track record, the OTP reception success rate for Facebook verification is approximately \textbf{85--95\%} when using recommended countries (Ethiopia, Indonesia, Philippines, India). The remaining 5--15\% are automatically refunded.
\end{successbox}
