% ══════════════════════════════════════════════
% CHAPTER 4: SETUP — WHAT THE CLIENT MUST DO
% ══════════════════════════════════════════════

\chapter{Setup Guide --- What You Must Do Before Deployment}

\section{How Far Are We From Deployment?}

\begin{successbox}
\textbf{Development Status: 100\% Complete.}

All 18 Python source files are written and compile without errors. The bot is fully functional. What remains is \textbf{configuration only} --- providing your specific API keys and Telegram credentials.
\end{successbox}

Here is the exact checklist of what remains:

\begin{table}[H]
\centering
\caption{Deployment Readiness Checklist}
\begin{tabularx}{\textwidth}{|c|l|c|X|}
\hline
\textbf{\#} & \textbf{Task} & \textbf{Status} & \textbf{Time Needed} \\
\hline
1 & Bot code development & \ding{51} Done & 0 minutes \\
\hline
2 & Database schema & \ding{51} Done & 0 minutes (auto-creates) \\
\hline
3 & Create Telegram Bot via BotFather & \ding{55} Pending & 2 minutes \\
\hline
4 & Create Telegram OTP Group & \ding{55} Pending & 2 minutes \\
\hline
5 & Create Telegram Channel & \ding{55} Pending & 2 minutes \\
\hline
6 & Register on 5sim.net & \ding{55} Pending & 5 minutes \\
\hline
7 & Fund 5sim.net account & \ding{55} Pending & 10--30 minutes \\
\hline
8 & Get your Telegram User ID & \ding{55} Pending & 1 minute \\
\hline
9 & Create .env file & \ding{55} Pending & 2 minutes \\
\hline
10 & Set up server (VPS) & \ding{55} Pending & 15--30 minutes \\
\hline
11 & Deploy and start bot & \ding{55} Pending & 5 minutes \\
\hline
\multicolumn{2}{|r|}{\textbf{Total Time Remaining:}} & & \textbf{45--75 minutes} \\
\hline
\end{tabularx}
\end{table}

\begin{infobox}
You are approximately \textbf{1 hour away} from having a fully operational bot. The majority of that time is account setup and server provisioning --- not coding.
\end{infobox}

% ──────────────────────────────────────────────
\section{Step 1: Create the Telegram Bot}

\begin{enumerate}
    \item Open Telegram and search for \texttt{@BotFather}
    \item Send \texttt{/newbot}
    \item BotFather asks: ``\textit{What name do you want for your bot?}''
    \item Enter: \texttt{Active Dream}
    \item BotFather asks: ``\textit{Choose a username for your bot}''
    \item Enter a unique username, e.g.: \texttt{ActiveDreamOTPBot}
    
    \begin{warningbox}
    The username must end with ``bot'' and be unique across all of Telegram. If your chosen name is taken, try variations like \texttt{ActiveDream\_OTP\_Bot} or \texttt{AD\_NumberBot}.
    \end{warningbox}
    
    \item BotFather will respond with your \textbf{Bot Token}. It looks like:
    
    \begin{lstlisting}[style=bashstyle]
    7123456789:AAFx8Kz3mN9bR2wQp1vL7dS5yH0jE4cW6uI
    \end{lstlisting}
    
    \item \textbf{Copy this token} --- you will need it for the \texttt{.env} file
    
    \item (Optional) Set bot description and profile picture via BotFather:
    \begin{itemize}
        \item \texttt{/setdescription} --- Set what users see before they start the bot
        \item \texttt{/setabouttext} --- Set the ``About'' section
        \item \texttt{/setuserpic} --- Upload a profile picture for the bot
    \end{itemize}
\end{enumerate}

% ──────────────────────────────────────────────
\section{Step 2: Get Your Telegram User ID}

Your User ID is needed so the bot knows who the admin is.

\begin{enumerate}
    \item Open Telegram and search for \texttt{@userinfobot}
    \item Send \texttt{/start}
    \item The bot will reply with your user information including your \textbf{numeric User ID}
    \item It looks like: \texttt{123456789}
    \item \textbf{Copy this number} --- this is your \texttt{ADMIN\_IDS} value
\end{enumerate}

\begin{tipbox}
You can have multiple admins. If you want user 111111111 and 222222222 as admins, set \texttt{ADMIN\_IDS=111111111,222222222} in the .env file.
\end{tipbox}

% ──────────────────────────────────────────────
\section{Step 3: Create the OTP Group}

\begin{enumerate}
    \item In Telegram, create a new group
    \item Name it: \textbf{Active Dream OTP}
    \item Add your bot (\texttt{@ActiveDreamOTPBot}) to the group
    \item Make the bot an \textbf{admin} of the group (so it can send messages)
    \item Get the group's Chat ID:
    \begin{enumerate}
        \item Add \texttt{@RawDataBot} to the group temporarily
        \item It will display the group info including the \textbf{Chat ID}
        \item The Chat ID looks like: \texttt{-1001234567890} (it starts with -100)
        \item \textbf{Copy this ID} --- this is your \texttt{OTP\_GROUP\_ID}
        \item You can remove @RawDataBot after getting the ID
    \end{enumerate}
    \item Create an invite link for the group --- this is your \texttt{OTP\_GROUP\_LINK}
\end{enumerate}

% ──────────────────────────────────────────────
\section{Step 4: Create the Update Channel}

\begin{enumerate}
    \item In Telegram, create a new \textbf{Channel}
    \item Name it: \textbf{Active Dream Channel}
    \item Add your bot as an admin of the channel
    \item Get the channel's public link (e.g., \texttt{https://t.me/ActiveDreamChannel})
    \item This is your \texttt{CHANNEL\_LINK}
\end{enumerate}

% ──────────────────────────────────────────────
\section{Step 5: Register on 5sim.net and Get API Key}

\begin{enumerate}
    \item Visit \href{https://5sim.net}{https://5sim.net}
    \item Register with your email
    \item Verify your email address
    \item Go to \textbf{Profile} $\rightarrow$ scroll to \textbf{API Key}
    \item Click \textbf{Generate API Key}
    \item \textbf{Copy the API key} --- this is your \texttt{FIVESIM\_API\_KEY}
\end{enumerate}

% ──────────────────────────────────────────────
\section{Step 6: Fund Your 5sim.net Account}

See Chapter 3, Section 3.4 for detailed funding instructions specific to Bangladesh.

\textbf{Minimum recommended starting balance: \$10 (approximately 1,200 BDT)}

% ──────────────────────────────────────────────
\section{Step 7: Create the .env Configuration File}

After completing all the steps above, you should have all the values needed. Create the \texttt{.env} file:

\begin{lstlisting}[style=envstyle, title=.env --- Your Configuration File]
# Telegram Bot Token (from BotFather)
BOT_TOKEN=7123456789:AAFx8Kz3mN9bR2wQp1vL7dS5yH0jE4cW6uI

# Your Telegram User ID (from @userinfobot)
ADMIN_IDS=123456789

# 5sim.net API Key (from 5sim.net profile)
FIVESIM_API_KEY=eyJhbGciOiJSUzUxMiIsInR5cCI6IkpXVCJ9...

# OTP Group (from @RawDataBot)
OTP_GROUP_ID=-1001234567890
OTP_GROUP_LINK=https://t.me/ActiveDreamOTP

# Channel
CHANNEL_LINK=https://t.me/ActiveDreamChannel

# Bot Name
BOT_NAME=Active Dream

# OTP Polling Settings (seconds)
OTP_CHECK_INTERVAL=5
OTP_MAX_WAIT=300
\end{lstlisting}

\begin{importantbox}
\textbf{SECURITY:} The \texttt{.env} file contains your secrets. \textbf{Never share it, never upload it to GitHub, never send it to anyone.} If compromised, someone could:
\begin{itemize}
    \item Control your bot
    \item Spend your 5sim.net balance
    \item Send messages as your bot
\end{itemize}
\end{importantbox}

% ──────────────────────────────────────────────
\section{Summary of Values You Need}

\begin{table}[H]
\centering
\caption{All Required Configuration Values}
\begin{tabularx}{\textwidth}{|l|l|X|}
\hline
\textbf{Variable} & \textbf{Source} & \textbf{Example} \\
\hline
BOT\_TOKEN & @BotFather & \texttt{7123456789:AAFx8K...} \\
\hline
ADMIN\_IDS & @userinfobot & \texttt{123456789} \\
\hline
FIVESIM\_API\_KEY & 5sim.net Profile & \texttt{eyJhbGci...} \\
\hline
OTP\_GROUP\_ID & @RawDataBot & \texttt{-1001234567890} \\
\hline
OTP\_GROUP\_LINK & Group invite link & \texttt{https://t.me/ActiveDreamOTP} \\
\hline
CHANNEL\_LINK & Channel link & \texttt{https://t.me/ActiveDreamChannel} \\
\hline
\end{tabularx}
\end{table}
