% ══════════════════════════════════════════════════════
% PART 1: COLLECTING CLIENT INFORMATION
% ══════════════════════════════════════════════════════

\chapter{Phase 1 --- Collect Client Information}

\section{Overview}

Before you can deploy the bot, you need \textbf{4 pieces of information} from your client. Without these, the bot cannot function. This phase involves \textbf{zero coding} --- you are simply gathering credentials.

\begin{infobox}
\textbf{Who is the Admin?} The admin is determined by a single value in the \texttt{.env} file called \texttt{ADMIN\_IDS}. Whoever's Telegram User ID is in that field becomes the bot admin. The admin can:
\begin{itemize}
    \item Approve/reject user access requests
    \item Add balance to users
    \item Ban/unban users
    \item Broadcast messages
    \item View statistics
\end{itemize}
To make your \textbf{client} the admin, you put \textbf{their} User ID there --- not yours.
\end{infobox}

\section{What You Need From the Client}

\begin{table}[H]
\centering
\caption{Required Information Checklist}
\begin{tabularx}{\textwidth}{|c|l|X|c|}
\hline
\textbf{\#} & \textbf{Item} & \textbf{How Client Gets It} & \textbf{Got It?} \\
\hline
1 & Bot Token & Create bot via @BotFather on Telegram & $\square$ \\
\hline
2 & Client User ID & Send /start to @userinfobot & $\square$ \\
\hline
3 & 5sim.net API Key & Register on 5sim.net, go to Profile & $\square$ \\
\hline
4 & OTP Group Chat ID & Add @RawDataBot to the group & $\square$ \\
\hline
\end{tabularx}
\end{table}

\section{Step-by-Step: Getting Each Item}

\subsection{Item 1: Bot Token (2 minutes)}

The client must create the bot under \textbf{their own} Telegram account. This way, the bot belongs to them.

\begin{stepbox}{Steps for the Client}
\begin{enumerate}[leftmargin=1.5cm]
    \item Open Telegram app (phone or desktop)
    \item Search for \texttt{@BotFather} and tap \textbf{Start}
    \item Send the message: \texttt{/newbot}
    \item BotFather asks: ``What name for your bot?''
    \begin{itemize}
        \item Client types: \texttt{Active Dream} (or whatever name they want)
    \end{itemize}
    \item BotFather asks: ``Choose a username''
    \begin{itemize}
        \item Client types: \texttt{ActiveDream\_OTP\_Bot} (must end with \texttt{bot})
        \item If taken, try: \texttt{ActiveDreamOTP\_Bot}, \texttt{AD\_Number\_Bot}, etc.
    \end{itemize}
    \item BotFather responds with a \textbf{Token} that looks like:
    \begin{lstlisting}[style=termstyle]
7123456789:AAFx8Kz3mN9bR2wQp1vL7dS5yH0jE4cW6uI
    \end{lstlisting}
    \item \textbf{Client copies this token and sends it to you}
\end{enumerate}
\end{stepbox}

\begin{warningbox}
The bot token is like a password. Tell the client: ``\textbf{This token controls the bot. Never share it publicly. Only send it to me privately.}''
\end{warningbox}

\subsection{Item 2: Client's Telegram User ID (30 seconds)}

\begin{stepbox}{Steps for the Client}
\begin{enumerate}[leftmargin=1.5cm]
    \item Open Telegram
    \item Search for \texttt{@userinfobot}
    \item Tap \textbf{Start} or send \texttt{/start}
    \item The bot replies with info including a number like:
    \begin{lstlisting}[style=termstyle]
Id: 987654321
    \end{lstlisting}
    \item \textbf{Client copies the number and sends it to you}
\end{enumerate}
\end{stepbox}

\begin{tipbox}
If you want \textbf{both you and the client} as admins, you'll use both IDs separated by a comma: \texttt{ADMIN\_IDS=987654321,1272625698}
\end{tipbox}

\subsection{Item 3: 5sim.net API Key (5 minutes)}

This is the service that provides real virtual phone numbers.

\begin{stepbox}{Steps for the Client}
\begin{enumerate}[leftmargin=1.5cm]
    \item Go to \url{https://5sim.net} in a web browser
    \item Click \textbf{Sign Up} / \textbf{Register}
    \item Register with email address
    \item Verify email
    \item After logging in, click on the \textbf{username/profile} icon (top right)
    \item Scroll down to the \textbf{``API Key''} section
    \item Click \textbf{``Generate API Key''}
    \item A long text appears starting with \texttt{eyJ...}
    \item \textbf{Client copies this and sends it to you}
\end{enumerate}
\end{stepbox}

\begin{importantbox}
The client \textbf{also needs to fund} their 5sim.net account with at least \textbf{\$10 USD} for the bot to buy real numbers. They can use Binance P2P (BDT to USDT) to fund it. See Chapter 3 of the main documentation for detailed funding instructions.

\textbf{Without funding, the bot will still work but will use mock/fake numbers.} This is fine for initial testing and demonstration.
\end{importantbox}

\subsection{Item 4: OTP Group Chat ID (3 minutes)}

When an OTP is received, the bot forwards it to a Telegram group for team visibility.

\begin{stepbox}{Steps for the Client}
\begin{enumerate}[leftmargin=1.5cm]
    \item Create a new \textbf{Group} in Telegram
    \item Name it: \textbf{Active Dream OTP} (or any name)
    \item Add the bot they created (e.g., \texttt{@ActiveDream\_OTP\_Bot}) to the group
    \item \textbf{Make the bot an admin} of the group (this is required so it can send messages)
    \item Now add \texttt{@RawDataBot} to the group
    \item RawDataBot will immediately post a message showing the group info
    \item Look for the line that says \textbf{``Chat ID''} --- it looks like:
    \begin{lstlisting}[style=termstyle]
"id": -1001234567890
    \end{lstlisting}
    \item \textbf{Client copies this number} (including the minus sign!) \textbf{and sends it to you}
    \item The client can now \textbf{remove @RawDataBot} from the group (it was only needed to get the ID)
\end{enumerate}
\end{stepbox}

\section{Message Template to Send Your Client}

Copy-paste this to your client on Telegram or WhatsApp:

\begin{lstlisting}[style=envstyle, title={Message to Client (Bangla)}]
Assalamu Alaikum ভাইয়া,

বটটা পুরোপুরি রেডি আছে। Deploy করার আগে 
আপনাকে ৪টা জিনিস করতে হবে:

1) Telegram-এ @BotFather এ গিয়ে /newbot দিন
   - নাম দিন: Active Dream
   - Username দিন (bot দিয়ে শেষ হতে হবে)
   - যে Token আসবে সেটা কপি করে দিন

2) Telegram-এ @userinfobot এ /start দিন
   - যে নম্বর আসবে সেটা কপি করে দিন

3) https://5sim.net এ একাউন্ট করুন
   - Profile > API Key > Generate
   - সেই API Key কপি করে দিন
   - (একাউন্টে $10 ঢুকাতে হবে - 
     Binance P2P দিয়ে USDT পাঠাবেন)

4) Telegram-এ একটা Group বানান 
   "Active Dream OTP" নামে
   - বটটা গ্রুপে যোগ করুন এবং Admin করুন
   - গ্রুপে @RawDataBot যোগ করুন
   - যে Chat ID আসবে (-100 দিয়ে শুরু) 
     সেটা দিন
   - তারপর RawDataBot বের করে দিন

এই ৪টা জিনিস পেলেই ১ ঘণ্টার মধ্যে 
বট লাইভ করে দিচ্ছি! ✅
\end{lstlisting}

\section{After You Receive the Information}

Once the client sends you all 4 items, you should have a list like this:

\begin{lstlisting}[style=envstyle, title={Your collected values (example)}]
Bot Token:   7123456789:AAFx8Kz3mN9bR2wQp1vL7dS5yH0jE4cW6uI
User ID:     987654321
API Key:     eyJhbGciOiJSUzUxMiIsInR5cCI6IkpXVCJ9...
Group ID:    -1001234567890
\end{lstlisting}

\begin{successbox}
You have everything you need! Now proceed to \textbf{Phase 2: Upload to GitHub}, then \textbf{Phase 3: Deploy on Railway}.
\end{successbox}
