\documentclass[a4paper,11pt]{article}

% ── Packages ────────────────────────────────────────
\usepackage[margin=1.8cm, top=1.5cm, bottom=1.5cm]{geometry}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{fontawesome5}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{array}
\usepackage{calc}

% ── Colors ──────────────────────────────────────────
\definecolor{brandDark}{HTML}{1A1A2E}
\definecolor{brandPurple}{HTML}{6C63FF}
\definecolor{brandLight}{HTML}{E8E6FF}
\definecolor{textGray}{HTML}{555555}
\definecolor{borderGray}{HTML}{DDDDDD}
\definecolor{successGreen}{HTML}{27AE60}
\definecolor{rowAlt}{HTML}{F8F7FF}

% ── Hyperlinks ──────────────────────────────────────
\hypersetup{
    colorlinks=true,
    linkcolor=brandPurple,
    urlcolor=brandPurple,
}

% ── No page numbers ────────────────────────────────
\pagestyle{empty}

% ── Custom commands ────────────────────────────────
\newcommand{\invoiceline}{\noindent\textcolor{borderGray}{\rule{\textwidth}{0.5pt}}\vspace{4pt}}

\begin{document}

% ══════════════════════════════════════════════════
% HEADER
% ══════════════════════════════════════════════════

\begin{tikzpicture}[remember picture, overlay]
    \fill[brandDark] (current page.north west) rectangle +(\paperwidth, -3.2cm);
\end{tikzpicture}

\vspace{-1.5cm}

\noindent
\begin{minipage}[t]{0.55\textwidth}
    \vspace{0pt}
    {\color{white}\fontsize{28}{34}\selectfont\bfseries INVOICE}\\[6pt]
    {\color{brandLight}\large Software Development Services}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.4\textwidth}
    \vspace{0pt}
    \raggedleft
    {\color{white}\large\bfseries NHM Development}\\[3pt]
    {\color{brandLight}\small Nafis Hossain Momen}\\
    {\color{brandLight}\small Software Developer}
\end{minipage}

\vspace{1.8cm}

% ══════════════════════════════════════════════════
% INVOICE META
% ══════════════════════════════════════════════════

\noindent
\begin{minipage}[t]{0.48\textwidth}
    {\small\color{textGray}\bfseries BILL TO}\\[4pt]
    {\large\bfseries Client}\\[2pt]
    {\color{textGray} Active Dream Project\\
    Telegram OTP Bot Commission}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.48\textwidth}
    \raggedleft
    {\small\color{textGray}\bfseries INVOICE DETAILS}\\[4pt]
    \begin{tabular}{r@{\hspace{8pt}}l}
        {\color{textGray}Invoice No:} & \textbf{NHM-2026-001} \\[2pt]
        {\color{textGray}Date:} & \textbf{May 16, 2026} \\[2pt]
        {\color{textGray}Due Date:} & \textbf{Upon Delivery} \\[2pt]
        {\color{textGray}Status:} & \textcolor{successGreen}{\textbf{DUE}} \\
    \end{tabular}
\end{minipage}

\vspace{0.6cm}
\invoiceline

% ══════════════════════════════════════════════════
% PROJECT SUMMARY
% ══════════════════════════════════════════════════

\vspace{0.2cm}
\noindent{\color{brandDark}\large\bfseries Project: Active Dream --- Telegram OTP Bot}

\vspace{0.2cm}
\noindent{\color{textGray}\small
A fully modular, production-ready private Telegram bot providing virtual phone numbers and automated OTP verification for 13+ services across 20+ countries. Includes admin panel, permission system, balance management, API integration, comprehensive documentation, and deployment support.}

\vspace{0.5cm}

% ══════════════════════════════════════════════════
% LINE ITEMS TABLE
% ══════════════════════════════════════════════════

\noindent
\begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}X c r r@{}}
\toprule
\rowcolor{brandDark}
{\color{white}\bfseries Description} & {\color{white}\bfseries Qty} & {\color{white}\bfseries Rate (BDT)} & {\color{white}\bfseries Amount (BDT)} \\
\midrule

% Item 1
\textbf{Telegram Bot Core Development} & 1 & & \\
{\small\color{textGray} Complete bot architecture: entry point, config loader,
database layer (SQLite), command routing, polling system.
19 Python source files with async architecture.} & & & \textbf{5,000} \\[4pt]

\rowcolor{rowAlt}
% Item 2
\textbf{Permission \& Access Control System} & 1 & & \\
\rowcolor{rowAlt}
{\small\color{textGray} Request Access flow, admin approve/reject notifications,
role-based decorators (@require\_approved, @require\_admin),
user status management (pending/approved/rejected/banned).} & & & \textbf{2,500} \\[4pt]

% Item 3
\textbf{Virtual Number \& OTP System} & 1 & & \\
{\small\color{textGray} 5sim.net API integration, abstract provider interface,
background OTP polling (asyncio), auto-refund on timeout,
service selection (13+ platforms), country selection (20+).} & & & \textbf{3,500} \\[4pt]

\rowcolor{rowAlt}
% Item 4
\textbf{Admin Dashboard \& Management Panel} & 1 & & \\
\rowcolor{rowAlt}
{\small\color{textGray} /admin command panel, real-time statistics, user management,
balance system (add/deduct/refund), /broadcast messaging,
/ban and /unban functionality, transaction logging.} & & & \textbf{2,500} \\[4pt]

% Item 5
\textbf{Mock Provider for Free Testing} & 1 & & \\
{\small\color{textGray} Complete mock SMS provider simulating number purchase and
OTP reception without any API costs. Auto-detection based
on .env configuration. Enables risk-free testing.} & & & \textbf{1,000} \\[4pt]

\rowcolor{rowAlt}
% Item 6
\textbf{Technical Documentation (38-Page PDF)} & 1 & & \\
\rowcolor{rowAlt}
{\small\color{textGray} Professional LaTeX documentation: project overview,
architecture diagrams, file-by-file explanation, database
schema, 5sim.net analysis, setup guide, deployment guide,
future improvements roadmap. 6 chapters + master compiler.} & & & \textbf{3,000} \\[4pt]

% Item 7
\textbf{Deployment Guide \& Support} & 1 & & \\
{\small\color{textGray} Step-by-step VPS deployment guide, systemd service
configuration, SSH setup instructions, troubleshooting
FAQ, delivery checklist. Ongoing deployment assistance.} & & & \textbf{1,500} \\[4pt]

\rowcolor{rowAlt}
% Item 8
\textbf{Testing \& Quality Assurance} & 1 & & \\
\rowcolor{rowAlt}
{\small\color{textGray} Syntax verification of all 19 files, live bot testing
on Telegram, flow verification (access request, number
purchase, OTP reception, admin panel), bug fixes.} & & & \textbf{1,000} \\

\midrule
\bottomrule
\end{tabularx}

\vspace{0.4cm}

% ══════════════════════════════════════════════════
% TOTALS
% ══════════════════════════════════════════════════

\noindent
\hfill
\begin{minipage}{0.45\textwidth}
\begin{tabularx}{\textwidth}{X r}
    {\color{textGray}Subtotal:} & \textbf{20,000 BDT} \\[4pt]
    {\color{textGray}Discount:} & {\color{successGreen}\textbf{-- 0 BDT}} \\[4pt]
    \midrule
    \\[-8pt]
    {\large\bfseries Total Due:} & {\large\color{brandPurple}\bfseries 20,000 BDT} \\[2pt]
    & {\small\color{textGray}(Approx. \$167 USD)} \\
\end{tabularx}
\end{minipage}

\vspace{0.6cm}
\invoiceline

% ══════════════════════════════════════════════════
% PAYMENT INFORMATION
% ══════════════════════════════════════════════════

\vspace{0.2cm}
\noindent{\color{brandDark}\large\bfseries \faMoneyBill\ Payment Methods}

\vspace{0.3cm}

\noindent
\begin{minipage}[t]{0.48\textwidth}
    \colorbox{brandLight}{%
        \parbox{\dimexpr\linewidth-2\fboxsep}{%
            \vspace{6pt}
            {\color{brandPurple}\bfseries \faMobile\ bKash (Personal)}\\[4pt]
            {\large\bfseries 01756003283}\\[3pt]
            {\small\color{textGray}Account: Nafis Hossain Momen}\\[2pt]
            {\small\color{textGray}Type: Send Money / Payment}
            \vspace{6pt}
        }%
    }
\end{minipage}%
\hfill
\begin{minipage}[t]{0.48\textwidth}
    \colorbox{brandLight}{%
        \parbox{\dimexpr\linewidth-2\fboxsep}{%
            \vspace{6pt}
            {\color{brandPurple}\bfseries \faUniversity\ Bank Transfer}\\[4pt]
            {\large\bfseries Islami Bank Bangladesh Ltd.}\\[3pt]
            {\small\color{textGray}A/C No: 20502266700184205}\\[2pt]
            {\small\color{textGray}A/C Name: Most. Faiza Akhter Surma}
            \vspace{6pt}
        }%
    }
\end{minipage}

\vspace{0.6cm}
\invoiceline

% ══════════════════════════════════════════════════
% DELIVERABLES SUMMARY
% ══════════════════════════════════════════════════

\vspace{0.2cm}
\noindent{\color{brandDark}\large\bfseries \faBoxOpen\ Deliverables Included}

\vspace{0.3cm}

\noindent
\begin{tabularx}{\textwidth}{@{}c X@{}}
    \textcolor{successGreen}{\faCheckCircle} & Complete source code (19 Python files, modular architecture) \\[3pt]
    \textcolor{successGreen}{\faCheckCircle} & Production-ready Telegram bot with async architecture \\[3pt]
    \textcolor{successGreen}{\faCheckCircle} & 5sim.net API integration + Mock provider for testing \\[3pt]
    \textcolor{successGreen}{\faCheckCircle} & Admin panel with full user and balance management \\[3pt]
    \textcolor{successGreen}{\faCheckCircle} & 38-page professional PDF documentation (LaTeX) \\[3pt]
    \textcolor{successGreen}{\faCheckCircle} & Step-by-step deployment guide with troubleshooting \\[3pt]
    \textcolor{successGreen}{\faCheckCircle} & VPS deployment support and initial setup assistance \\[3pt]
    \textcolor{successGreen}{\faCheckCircle} & .env configuration template with full instructions \\
\end{tabularx}

\vspace{0.5cm}
\invoiceline

% ══════════════════════════════════════════════════
% FOOTER / TERMS
% ══════════════════════════════════════════════════

\vspace{0.2cm}
\noindent{\color{brandDark}\bfseries Terms \& Conditions}

\vspace{0.2cm}
\noindent{\small\color{textGray}
\begin{enumerate}
    \itemsep2pt
    \item Payment is due upon delivery and successful demonstration of the bot.
    \item This invoice covers development, documentation, and initial deployment support.
    \item Ongoing server costs (VPS: \~400 BDT/month, 5sim.net: variable) are the client's responsibility.
    \item Minor bug fixes within 7 days of delivery are included at no extra charge.
    \item Feature additions or major modifications after delivery will be quoted separately.
    \item Source code ownership transfers to the client upon full payment.
\end{enumerate}
}

\vspace{0.4cm}

\begin{center}
    {\color{textGray}\small Thank you for your business!}\\[4pt]
    {\color{brandPurple}\bfseries NHM Development} {\color{textGray}|} {\small\color{textGray} Nafis Hossain Momen} {\color{textGray}|} {\small\color{textGray} May 2026}
\end{center}

\end{document}
